Should I Airbnb My Property?

### 2017-03-09 abb_Writeup.Rmd
moving analyses to analysis

    data.path <- 'alternate data path'
    code.path <- 'alternate data path'

@@

```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=TRUE}

@@

```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide'}

@@

```{r plot_pt, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='\\label{typecomp}Property Type by Tenure'}

@@

```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals'}

@@

```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure by Type'}

@@

After removing property level observations that are missing price data, we plot the distribution of the rates and rents.  In Figure 4 we see that most long-term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night. We filter the property level data accordingly. We also filter the short-term daily data to include only those observations with nightly rates between \$50 and \$500.

```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents'}

@@

```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'}

@@

```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='\\label{coretable}List of Core Suburbs'}

@@

```{r load_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}

@@

```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.ext='png'}

@@

```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts'}

@@

```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='\\label{revdens}Comparison of Revenue Distributions', fig.lp='revdens'}

  ggplot(revdens.data, aes(x=revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
    scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
    #ggtitle('Annual Revenues by Tenure Type') +
    xlab('\nAnnual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20k', '$40k', '$60k'))+
    theme(legend.position='none',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000)) +
    facet_wrap(~tenure)

@@

We will begin our analysis by making a comparison of the short and long-term markets at the metropolitan level.  Of our sample of 5,783 short-term rental units, 1,600 or 27.7\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.

@@

```{r plot_occ_metro, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'}

@@

```{r plot_svmr_metro, fig.width=8, fig.height=4, echo=FALSE, warning=FALSE, fig.align='center', fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'}

@@

  rate.hm <- abbHeatMap(str.data.ic,
                x.field='occ.rate',
                y.field='med.rate',
                pref.field='str.ext.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm <- rate.hm + ylab('Nightly Rate')

@@

  rate.hm.svm <- abbHeatMap(str.data.ic,
                            x.field='occ.rate',
                            y.field='med.rate',
                            pref.field='str.ext.pref',
                            svm=T, 
                            alpha.count=F,
                            add.points=T,
                            fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm.svm <- rate.hm.svm + ylab('Nightly Rate')

@@

  qtl.hm <- abbHeatMap(str.data.ic,
                x.field='occ.qtl',
                y.field='rate.qtl',
                pref.field='str.ext.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm <- qtl.hm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')

@@

  qtl.hm.svm <- abbHeatMap(str.data.ic,
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')

@@

```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}

 ## Create dataset

  type.data.ic <- str.data.ic

  # Id the types
  apt.id <- which(str.data.ic$type == 'Apartment')
  house.id <- which(str.data.ic$type == 'House')

  # Recalculate the percentiles
  type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id],
                                      return.type='rank')
  type.data.ic$occ.qtl[house.id] <- makeWtdQtl(
    type.data.ic$occ.rate[house.id], return.type='rank')

  type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id],
                                  return.type='rank')
  type.data.ic$rate.qtl[house.id] <- makeWtdQtl(
    type.data.ic$med.rate[house.id], return.type='rank')

 ## Calc the occ rate numbers

  ptrocc <- abbPrefPlot(type.data.ic,
                         x.field='occ.rate',
                         split.field='type',
                         smooth=TRUE,
                         smooth.span=.5 ,
                         spl.col=c('black', 'grey40'))

  ptqocc <- abbPrefPlot(type.data.ic,
                         x.field='occ.qtl',
                         split.field='type',
                         smooth=TRUE,
                         smooth.span=.5 ,
                         spl.col=c('black', 'grey40'))

```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}

@@

  ptr.occ <- ggplot(ptrocc$data,
                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate') +
    scale_color_manual(values=c('black', 'grey60'),
                       name='') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom') + 
    ggtitle('Raw Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

@@

  ptq.occ <- ggplot(ptqocc$data,
                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate (Pcntl)') +
    scale_color_manual(values=c('black', 'grey60'),
                       name='') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25th', '50th', '75th', '100th')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom') + 
    ggtitle('Percentile Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

@@

  house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
                                          'House', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5])) +
  theme(legend.position='none') +
  annotate("text", x = 50, y = 50, label = "Houses", size=9) +
  ylab('Nightly Rate (Pcntl)') +
  xlab('Occupancy Rate (Pcntl)')

@@

  apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
                                          'Apartment', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
  annotate("text", x = 50, y = 50, label = "Apartments", size=9)+
  ylab('Nightly Rate (Pcntl)') +
  xlab('Occupancy Rate (Pcntl)')

@@

Next, we divide the data into the five geographic sub-market shown in \autoref{pointmaps}. Within the City-Core, approximately one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.  That figure drops to one in four for beach and rural properties, one in six for other city location and about one in nine for suburban locations.

```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'}

 # Make Basic comparison table
  pref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                   split.field='sub.mrkt')

@@

 # Limit to the extrapolated pref type
  pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ]
  pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
  pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%')

@@

There is a noticable variability in the relationship between occupancy rates and short-term preference across the submarkets. For raw rates (\autoref{smocc}, left panel), rural properties can acheive short-term preference with lower occupancies than the other areas. This may be due to the relatively low long-term rental rates in the more rural areas coupled with high short-term rates for homes in wine country or near the mountainous terrain east of the city. Transforming to percentiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the others, with suburban and city as the most difficult markets.  
```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}

 ## Build data

  subm.data.ic <- str.data.ic

  # Get IDs
  cc.id <- which(str.data.ic$sub.mrkt == 'city-core')
  city.id <- which(str.data.ic$sub.mrkt == 'city')
  sub.id <- which(str.data.ic$sub.mrkt == 'suburban')
  rural.id <- which(str.data.ic$sub.mrkt == 'rural')
  beach.id <- which(str.data.ic$sub.mrkt == 'beach')

  # Recalc the percentiles
  subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id],
                                      return.type='rank')
  subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id],
                                  return.type='rank')

  subm.data.ic$occ.qtl[city.id] <- makeWtdQtl(
      subm.data.ic$occ.rate[city.id], return.type='rank')
  subm.data.ic$rate.qtl[city.id] <- makeWtdQtl(
    subm.data.ic$med.rate[city.id], return.type='rank')

  subm.data.ic$occ.qtl[sub.id] <- makeWtdQtl(subm.data.ic$occ.rate[sub.id],
                                      return.type='rank')
  subm.data.ic$rate.qtl[sub.id] <- makeWtdQtl(subm.data.ic$med.rate[sub.id],
                                  return.type='rank')

  subm.data.ic$occ.qtl[rural.id] <- makeWtdQtl(subm.data.ic$occ.rate[rural.id],
                                      return.type='rank')
  subm.data.ic$rate.qtl[rural.id] <- makeWtdQtl(subm.data.ic$med.rate[rural.id],
                                  return.type='rank')

  subm.data.ic$occ.qtl[beach.id] <- makeWtdQtl(subm.data.ic$occ.rate[beach.id],
                                      return.type='rank')
  subm.data.ic$rate.qtl[beach.id] <- makeWtdQtl(subm.data.ic$med.rate[beach.id],
                                  return.type='rank')

@@

 ## Create plot data

  smrocc <- abbPrefPlot(subm.data.ic,
                        x.field='occ.rate',
                        split.field='sub.mrkt',
                        smooth=TRUE,
                        smooth.span=.5 ,
                        spl.col=sm.col)

  smqocc <- abbPrefPlot(subm.data.ic,
                         x.field='occ.qtl',
                         split.field='sub.mrkt',
                         smooth=TRUE,
                         smooth.span=.5 ,
                         spl.col=sm.col)

@@

  smr.occ <- ggplot(smrocc$data,
                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate') +
    scale_color_manual(values=sm.col,
                       name='') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom') + 
    ggtitle('Raw Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

  smq.occ <- ggplot(smqocc$data,
                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate (Pcntl)') +
    scale_color_manual(values=sm.col,
                       name='') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25th', '50th', '75th', '100th')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom') + 
    ggtitle('Percentile Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

@@

```{r build_svm_geo, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'}

@@

  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
                                          'city-core', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5])) +
  theme(legend.position='none') +
    ylab('') +
    xlab('') +
  annotate("text", x = 50, y = 50, label = "City-Core", size=9)

  city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
                                          'city', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('') +
    xlab('')+
  annotate("text", x = 50, y = 50, label = "City", size=9)

  sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
                                          'suburban', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('') +
    xlab('')+
  annotate("text", x = 50, y = 50, label = "Suburban", size=9)

  rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
                                          'rural', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('') +
    xlab('')+
  annotate("text", x = 50, y = 50, label = "Rural", size=9)

  beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
                                          'beach', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('') +
    xlab('')+
  annotate("text", x = 50, y = 50, label = "Beach", size=9)

@@

```{r log_model, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short-Term Preference'}

@@

  # Extract diagnostics
  str.dx <- logDx(pref.models[[1]], str.data.ic, str.data.ic$str.ext.pref)
  sm.dx <- logDx(pref.models[[2]], str.data.ic, str.data.ic$str.ext.pref)
  host.dx <- logDx(pref.models[[3]], str.data.ic, str.data.ic$str.ext.pref)

@@

  full.table <- rbind(full.table, diag.table)

@@

  pot.data.ic <- str.data.ic

>>>>

    data.path <- 'alternate data path'
    code.path <- 'alternate code path'
    fig.path <- 'alternate fig path'

@@

```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=FALSE}

@@

```{r set_constants, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}

@@

```{r plot_pt, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='\\label{typecomp}Property Type by Tenure'}

@@

```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals'}

@@

```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure by Type'}

@@

After removing property level observations that are missing price data, we plot the distribution of the rates and rents.  In \autoref{rrdist} we see that most long-term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night. We filter the property level data accordingly. We also filter the short-term daily data to include only those observations with nightly rates between \$50 and \$500.

```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='\\label{rrdist}Distribution of Rates and Rents'}

@@

```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'}

@@

```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE}

@@

```{r load_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}

@@

```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=5, fig.height=10, fig.cap='\\label{pointmaps}Location Maps', fig.ext='png'}

@@

```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='\\label{smcounts}Submarket Observation Counts'}

@@

```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='\\label{revdens}Comparison of Revenue Distributions'}

  ggplot(revdens.data, aes(x=revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
    scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
    xlab('\nAnnual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20k', '$40k', '$60k'))+
    theme(legend.position='none',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000)) +
    facet_wrap(~tenure)

@@

We will begin our analysis by making a comparison of the short and long-term markets at the metropolitan level.  Of our sample of 5,783 short-term rental units, 1,600 or 31.6\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.

@@

```{r plot_occ_metro, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'}

@@

```{r plot_svmr_metro, fig.width=8, fig.height=4, echo=FALSE, warning=FALSE, fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'}

@@

  rate.hm <- abbHeatMap(str.data.ic,
                x.field='occ.rate',
                y.field='med.rate',
                pref.field='str.act.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm <- rate.hm + ylab('Nightly Rate')

@@

  rate.hm.svm <- abbHeatMap(str.data.ic,
                            x.field='occ.rate',
                            y.field='med.rate',
                            pref.field='str.act.pref',
                            svm=T, 
                            alpha.count=F,
                            add.points=T,
                            fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm.svm <- rate.hm.svm + ylab('Nightly Rate')

@@

  qtl.hm <- abbHeatMap(str.data.ic,
                x.field='occ.qtl',
                y.field='rate.qtl',
                pref.field='str.act.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm <- qtl.hm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')

@@

  qtl.hm.svm <- abbHeatMap(str.data.ic,
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm.svm <- qtl.hm.svm + ylab('Nightly Rate (Pcntl)') + xlab('Occupancy Rate (Pcntl)')

@@

<!-- ```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->

<!--  ## Create dataset -->

<!--   type.data.ic <- str.data.ic -->

<!--   # Id the types -->
<!--   apt.id <- which(str.data.ic$type == 'Apartment') -->
<!--   house.id <- which(str.data.ic$type == 'House') -->

<!--   # Recalculate the percentiles -->
<!--   type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id], -->
<!--                                       return.type='rank') -->
<!--   type.data.ic$occ.qtl[house.id] <- makeWtdQtl( -->
<!--     type.data.ic$occ.rate[house.id], return.type='rank') -->

<!--   type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id], -->
<!--                                   return.type='rank') -->
<!--   type.data.ic$rate.qtl[house.id] <- makeWtdQtl( -->
<!--     type.data.ic$med.rate[house.id], return.type='rank') -->

<!--  ## Calc the occ rate numbers -->

<!--   ptrocc <- abbPrefPlot(type.data.ic, -->
<!--                          x.field='occ.rate', -->
<!--                          split.field='type', -->
<!--                          smooth=TRUE, -->
<!--                          smooth.span=.5 , -->
<!--                          spl.col=c('black', 'grey40')) -->

<!--   ptqocc <- abbPrefPlot(type.data.ic, -->
<!--                          x.field='occ.qtl', -->
<!--                          split.field='type', -->
<!--                          smooth=TRUE, -->
<!--                          smooth.span=.5 , -->
<!--                          spl.col=c('black', 'grey40')) -->

<!-- ``` -->

```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}

@@

  ptr.occ <- ggplot(rawocc.type$data,
                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate') +
    scale_color_manual(values=c('black', 'grey60'),
                       name='') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom') + 
    ggtitle('Raw Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

@@

  ptq.occ <- ggplot(pctocc.type$data,
                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate (Pcntl)') +
    scale_color_manual(values=c('black', 'grey60'),
                       name='') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25th', '50th', '75th', '100th')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom') + 
    ggtitle('Percentile Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

@@

  house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
                                          'House', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5])) +
  theme(legend.position='none') +
  annotate("text", x = 50, y = 50, label = "Houses", size=9) +
  ylab('Nightly Rate (Pcntl)') +
  xlab('Occupancy Rate (Pcntl)')

@@

  apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
                                          'Apartment', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
  annotate("text", x = 50, y = 50, label = "Apartments", size=9)+
  ylab('Nightly Rate (Pcntl)') +
  xlab('Occupancy Rate (Pcntl)')

@@

Next, we divide the data into the five geographic sub-market shown in \autoref{pointmaps}. Within the City-Core, greater than one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.  That figure drops to three in ten for rural, one in four for beach , one in fix for other city location and about one in six for suburban locations.

```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, echo=FALSE}

 # Make Basic comparison table
  pref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                   split.field='geo.mrkt')

@@

 # Limit to the extrapolated pref type
  pref.table <- pref.table[pref.table$rev.type == 'Actual', ]
  pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
  pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%')

@@

There is a noticable variability in the relationship between occupancy rates and short-term preference across the submarkets. For raw rates (\autoref{smocc}, left panel), rural properties can acheive short-term preference with lower occupancies than the other areas. This may be due to the relatively low long-term rental rates in the more rural areas coupled with high short-term rates for homes in wine country or near the mountainous terrain east of the city. Transforming to percentiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the others, with suburban and city as the most difficult markets.

@@

@@

  smr.occ <- ggplot(rawocc.geo$data,
                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate') +
    scale_color_manual(values=sm.col,
                       name='') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom') + 
    ggtitle('Raw Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

  smq.occ <- ggplot(pctocc.geo$data,
                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate (Pcntl)') +
    scale_color_manual(values=sm.col,
                       name='') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25th', '50th', '75th', '100th')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom') + 
    ggtitle('Percentile Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

@@

```{r build_svm_geo, warning=FALSE, message=FALSE, echo=FALSE}

@@

  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'city-core', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5])) +
  theme(legend.position='none') +
    ylab('') +
    xlab('') +
  annotate("text", x = 50, y = 50, label = "City-Core", size=9)

  city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'city', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('') +
    xlab('')+
  annotate("text", x = 50, y = 50, label = "City", size=9)

  sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'suburban', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('') +
    xlab('')+
  annotate("text", x = 50, y = 50, label = "Suburban", size=9)

  rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'rural', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('') +
    xlab('')+
  annotate("text", x = 50, y = 50, label = "Rural", size=9)

  beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'beach', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('') +
    xlab('')+
  annotate("text", x = 50, y = 50, label = "Beach", size=9)

@@

```{r log_model, echo=FALSE, message=FALSE, comment=FALSE}

@@

  # Extract diagnostics
  str.dx <- logDx(pref.models[[1]], str.data.ic, str.data.ic$str.act.pref)
  sm.dx <- logDx(pref.models[[2]], str.data.ic, str.data.ic$str.act.pref)
  host.dx <- logDx(pref.models[[3]], str.data.ic, str.data.ic$str.act.pref)

@@

  full.table <- rbind(full.table, diag.table)
```

```{r table_logmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE}

@@
